Effects of Reynolds Number on the Energy Conversion and Near-Wake Dynamics of a High Solidity Vertical-Axis Cross-Flow Turbine

### 2016-01-21 paper.tex
Remove empty line
Full --> complete
Use color on performance curve figures

Full-power and rotor drag (also known as thrust) coefficient curves for various
Reynolds numbers are plotted in Figures~\ref{fig:cp-curves} and
\ref{fig:cd-curves}, respectively. In general, maximum $C_P$ increases
with Reynolds number. The power coefficient curves also show a slight downward
shift in the optimal tip speed ratio (peak~performance) with increasing Reynolds
number, from about $\lambda \approx$ 2.0 to 1.9. This is caused by the stall
delay from a more turbulent boundary layer on the blade suction side. There is
essentially no change in the shape of the drag coefficient curves, merely a
slight upward shift in $C_D$ with increasing~ $Re$.

@@

\caption{\hl {Mean} power coefficient curves plotted for multiple Reynolds numbers.}
%is it better to mark different color to the lines?
\label{fig:cp-curves}
\end{figure}
\unskip

@@

\caption{\hl {Mean} rotor drag coefficient curves plotted for multiple Reynolds
 numbers.}
 % is it better to mark different color to the lines?

>>>>

Complete power and rotor drag (also known as thrust) coefficient curves for
various Reynolds numbers are plotted in Figures~\ref{fig:cp-curves} and
\ref{fig:cd-curves}, respectively. In general, maximum $C_P$ increases with
Reynolds number. The power coefficient curves also show a slight downward shift
in the optimal tip speed ratio (peak~performance) with increasing Reynolds
number, from about $\lambda \approx$ 2.0 to 1.9. This is caused by the stall
delay from a more turbulent boundary layer on the blade suction side. There is
essentially no change in the shape of the drag coefficient curves, merely a
slight upward shift in $C_D$ with increasing~ $Re$.

@@

    \caption{Mean power coefficient curves plotted for multiple Reynolds
        numbers.}

    \label{fig:cp-curves}
\end{figure}
\unskip

@@

    \caption{Mean rotor drag coefficient curves plotted for multiple Reynolds
        numbers.}
